Research Report

### 2023-02-28 tex/paper-acts/main.tex
Misc update

\documentclass{article}
\usepackage{babel}
\usepackage[includefoot]{geometry}
\usepackage{/home/user1/code/tex/sty}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{floatrow}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[backend=bibtex]{biblatex}
\addbibresource{bib.bib}
\floatsetup[figure]{objectset=centering}
\floatsetup[subfigure]{objectset=centering}
\hypersetup{colorlinks=true,citecolor=black,linkcolor=black}
\setlength{\parindent}{0pt}
\title{Research Report}
\author{Agustin Romero\thanks{ar1@stanford.edu}}

@@

\newcommand{\figpic}[3]{
\begin{figure}[H]
\begin{center}
\pic{#1}{#2}
\caption{#3}
\end{center}
\end{figure}}

\newcommand{\figtab}[3]{
\begin{table}[H]
\begin{tabular}{#1}
#2
\end{tabular}
\caption{#3}
\end{table}}

\n{abseta}{$|\eta|<$}
\n{ttbar}{$t\bar{t}$~}
\n{qqbar}{$q\bar{q}$~}
\newcommand{\romax}[0]{_{\textrm{max}}}
\newcommand{\romin}[0]{_{\textrm{min}}}
\newcommand{\pt}[0]{p_\textrm{T}}

@@

\figpic{5cm}{2.png}{Example of a track which passes from the barrel to the end cap. As $|\eta|$ lowers the track's points rightward in this diagram. These tracks are more difficult to reconstruct.}

@@

\section{Simulation}

@@

\begin{itemize}
\item Four cylindrical barrel layers of radii 34 mm, 70 mm, 116 mm, 172 mm
\item Barrel: 14 sensors per stave, cooling pipe surrounded by carbon foam, 2492 total
\item Pixel endcaps: disks at ±z 620 mm, 720 mm, 840 mm, 980 mm, 1120 mm, 1320 mm 1520 mm
\item Rings: 2 rings: 24, 36 modules, 420 sensors per endcap
\end{itemize}

@@

\begin{itemize}
\item Four barrel layers at r 260 mm, 360 mm, 500 mm, 660 mm
\item 40 to 102 staves, 21 sensors each
\item Endcaps disks at ±z 1300 mm, 1550 mm, 1850 mm, 2200 mm, 2550 mm, 2950 mm
\item Three rings of 42, 756 sensors in total
\end{itemize}

@@

\begin{itemize}
\item Two barrel layers at r 820 mm, 1020 mm, 60/80 staves of 21 sensors
\item Silicon sensors on kapton boards, carbon foam blocks, titanium cooling pipes
\item Endcaps disks at ±z 1300 mm, 1600 mm, 1900 mm, 2250 mm, 2600 mm, 3000 mm
\item Two rings of 48×2 sensors
\end{itemize}

A \ita{sequence} is an ordered list of algorithms beginning at event generation, through CKF reconstruction, and ending at the CKF efficiency analyzer. A \ita{trial} is one sequence which generates only one event using one set of parameters. A \ita{score} is a number calculated given the efficiencies from one trial.

\figtab{l l}{Pileup & 10\\
Vertex x-axis $\sigma$ [mm] & 0.0125\\
Vertex y-axis $\sigma$ [mm] & 0.0125\\
Vertex z-axis $\sigma$ [mm] & 55.5\\
Vertex t-axis $\sigma$ [ns] & 5}{Parameters used for event generation of vertices.}

% \figtab{l l}{Truth Seed Range $\pt$ [MeV] & 500\\
% r [mm] & 200\\
% \Delta r & Optimized from }

The following equations are used to evaluate the performance of the CKF algorithm. The default parameters used for tracking is used below. Most of these parameters were originally hand tuned. Next, they will be optimized.

@@

\qqbar $\rightarrow$ \ttbar events were simulated at energy 14 TeV, with 140 pileup particles, using Pythia, and tracked using ACTS.

The event generator used was Pythia.

@@

These are equations used for evaluating the CKF reconstruction algorithm. Specifically we are interested in \eqref{score}, \eqref{eff}, \eqref{trackfakerate}, and \eqref{trackduplicaterate}.

@@

\subsection{\label{spnfuad}Simulation Parameters}

@@

\e{score=efficiency}

@@

\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/grid.png}{Efficiency using the optimized parameters.}

@@

\e{score=efficiency}
\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Plot of score per trial}
\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/parameter_per_trial/grid.png}{Parameters per trial.}
\figpic{9cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/efficiency_per_trial/grid.png}{Efficiency per trial.}

@@

\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/grid.png}{Efficiency using the optimized parameters.}

@@

\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/grid.png}{Efficiency using the optimized parameters.}

@@

\e{score=eff_particles - fakerate_tracks - duplicaterate_tracks / 5}

@@

\figpic{9cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/grid.png}{Efficiency using the optimized parameters.}

@@

\e{score=particle eff - track eff / 2 - track duplicates / 4}

@@

\figpic{9cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/grid.png}{Efficiency using the optimized parameters.}

>>>>

\documentclass{article}
\usepackage{babel}
\usepackage[includefoot]{geometry}
\usepackage{/home/user1/code/tex/sty}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{floatrow}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[backend=bibtex]{biblatex}
\addbibresource{bib.bib}
\floatsetup[figure]{objectset=centering}
\floatsetup[subfigure]{objectset=centering}
\hypersetup{colorlinks=true,citecolor=black,linkcolor=black}
\setlength{\parindent}{0pt}
\title{Research Report}
\author{Agustin Romero\thanks{ar1@stanford.edu}}

@@

\newcommand{\figpic}[3]{
\begin{figure}[H]
\begin{center}
\pic{#1}{#2}
\caption{#3}
\end{center}
\end{figure}}
\n{sco}{\rom{score}}
\n{peff}{\rom{particle efficiency}}
\n{pdup}{\rom{particle duplicate rate}}
\n{pfak}{\rom{particle fake rate}}
\n{teff}{\rom{track efficiency}}
\n{tdup}{\rom{track duplicate rate}}
\n{tfak}{\rom{track fak rate}}
\n{abseta}{$|\eta|<$}
\n{ttbar}{$t\bar{t}$~}
\n{qqbar}{$q\bar{q}$~}
\newcommand{\romax}[0]{_{\textrm{max}}}
\newcommand{\romin}[0]{_{\textrm{min}}}
\newcommand{\pt}[0]{p_\textrm{T}}
\newcommand{\figtab}[3]{
\begin{table}[H]
\begin{tabular}{#1}
#2
\end{tabular}
\caption{#3}
\end{table}}

@@

\figpic{5cm}{2.png}{Diagram of a track which passes from the barrel to the end cap. As $|\eta|$ lowers the track's points rightward in this diagram. These tracks are more difficult to reconstruct.}

@@

@@

\begin{itemize}
\item Four cylindrical barrel layers of radii 34 mm, 70 mm, 116 mm, 172 mm
\item Barrel: 14 sensors per stave, cooling pipe surrounded by carbon foam, 2492 total
\item Pixel endcaps: disks at ±z 620 mm, 720 mm, 840 mm, 980 mm, 1120 mm, 1320 mm 1520 mm
\item Rings: 2 rings: 24, 36 modules, 420 sensors per endcap
\end{itemize}

@@

\begin{itemize}
\item Four barrel layers at r 260 mm, 360 mm, 500 mm, 660 mm
\item 40 to 102 staves, 21 sensors each
\item Endcaps disks at ±z 1300 mm, 1550 mm, 1850 mm, 2200 mm, 2550 mm, 2950 mm
\item Three rings of 42, 756 sensors in total
\end{itemize}

@@

\begin{itemize}
\item Two barrel layers at r 820 mm, 1020 mm, 60/80 staves of 21 sensors
\item Silicon sensors on kapton boards, carbon foam blocks, titanium cooling pipes
\item Endcaps disks at ±z 1300 mm, 1600 mm, 1900 mm, 2250 mm, 2600 mm, 3000 mm
\item Two rings of 48×2 sensors
\end{itemize}

Some terminology is described here. A \ita{sequence} is an ordered list of algorithms beginning at event generation, through CKF reconstruction, and ending at the CKF efficiency analyzer. A \ita{trial} is one sequence with one set of parameters. A \ita{score} is a number calculated given the efficiencies from one trial.

\figtab{l l}{Pileup & 100\\
Vertex x-axis $\sigma$ [mm] & 0.0125\\
Vertex y-axis $\sigma$ [mm] & 0.0125\\
Vertex z-axis $\sigma$ [mm] & 55.5\\
Vertex t-axis $\sigma$ [ns] & 5}{Parameters used for event generation of vertices.}

\figtab{l l}{Truth Seed Range $\pt$ [MeV] & 500\\
r [mm] & 200\\
\Delta r & Optimized}

The following equations are used to evaluate the performance of the CKF algorithm. The default parameters used for tracking is used below.

@@

The event generator used was Pythia. \qqbar $\rightarrow$ \ttbar events were simulated at energy 14 TeV, with 100 pileup particles, using Pythia, and tracked using ACTS.

@@

These are equations used for evaluating the CKF reconstruction algorithm.

@@

\subsection{\label{spnfuad}Summary of Simulation Parameters}

@@

\e{\sco=\peff}

@@

\figpic{7cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/dup.png}{Plot of score per trial}
\figpic{7cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/eff.png}{Parameters per trial.}
\figpic{7cm}{/home/user1/time/2023-02-22/2023-02-22-13-30/compare-4/fak.png}{Efficiency per trial.}

@@

\e{\sco=\peff}
\figpic{6\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/score.png}{Plot of score per trial}
\figpic{9\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/parameter_per_trial/grid.png}{Parameters per trial.}
\figpic{9\cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/efficiency_per_trial/grid.png}{Efficiency per trial.}

@@

\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/dup.png}{Plot of score per trial}
\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/eff.png}{Parameters per trial.}
\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-04-19/compare-4/fak.png}{Efficiency per trial.}

@@

\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-02-45/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\e{\sco=\preff - \tfak - \tdup/5}

@@

\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{7cm}{/home/user1/time/2023-02-23/2023-02-23-10-07/compare-1/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}

@@

\e{\sco=\peff - \tfak / 2 -\tdup/4}

@@

\figpic{7cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/dup.png}{Track duplicate fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{7cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/eff.png}{Track efficiency fraction as function of $\eta$, $\phi$, and $\pt$.}
\figpic{7cm}{/home/user1/time/2023-02-24/2023-02-24-07-07/compare-2/fak.png}{Track fake fraction as function of $\eta$, $\phi$, and $\pt$.}
